---
output: word_document
---
---
# Reproducible Research Course Project 1

###Loading and processing the data
```{r}
setwd("~/Desktop/coursera/reproducible_research/project1")
mydata <- read.csv("activity.csv")
```
###What is mean total number of steps taken per day?
For this, we will ignore the missing values in the dataset.

###1. Calculate the total number of steps taken per day.
```{r}
steps_per_day <- tapply(mydata$steps, mydata$date, sum, na.rm=TRUE)
```

###2. Histogram of the total number of steps taken per day

```{r}
hist(steps_per_day, xlab='Total steps per day', ylab='Frequency', col="blue")
```

###3. Calculate mean and median total number of steps taken per day

```{r}
s_mean <- mean(steps_per_day)
s_median <- median(steps_per_day)
```
###What is the average daily activity pattern?
```{r}
average_daily_activity <- aggregate(x=list(meanSteps=mydata$steps), by=list(interval=mydata$interval), FUN=mean, na.rm=TRUE)
```
###1. Make a time series plot of the 5-minute interval and the average number of steps taken
```{r}
library(ggplot2)
ggplot(data=average_daily_activity, aes(x=interval, y=meanSteps)) +
    geom_line() +
    xlab("5-minute interval") +
    ylab("average number of steps")
```

###2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
maxSteps <- which.max(average_daily_activity$meanSteps)
Timemaxsteps <- gsub("([0-9]{1,2})([0-9]{2})", "\\1:\\2",average_daily_activity[maxSteps,'interval'])
```
###Imputing missing values
1. Calculate and report the total number of missing values in the dataset.

2. Devise a strategy for  lling in all of the missing values in the dataset.

3. Create a new dataset that is equal to the original dataset but with the missing data  lled in.

4. Make a histogram of the total number of steps taken each day.
Combined codes for 1 through 4 are as follows:
```{r}
missing <- length(which(is.na(mydata$steps)))
newdata <- mydata
newdata$steps[is.na(newdata$steps)] <- median(mydata$steps, na.rm=TRUE)
inputednewdata <- aggregate(steps ~ date, data=newdata, sum, na.rm=TRUE)
hist(inputednewdata$steps, xlab='Total steps per day (new)', ylab='Frequency', col="blue")
```

###Are there differences in activity patterns between weekdays and weekends?

###1. Create a new factor variable in the dataset with two levels – “weekday” and “weekend” indicating whether a given date is a weekday or weekend day.
```{r}
newdata$date <- as.Date(newdata$date)
newdata$dayname <- weekdays(newdata$date)
newdata$weekend <- as.factor(ifelse(newdata$dayname == "Saturday" | newdata$dayname == "Sunday", "weekend", "weekday"))
```
###2. Make a panel plot containing a time series plot 
```{r}
library(lattice)
plotdata <- aggregate(steps ~ interval + weekend, newdata, mean)
xyplot(steps ~ interval | factor(weekend), data=plotdata, type="l", col="black")
```
    